\sysfull

### 2018-04-10 paper/paper.tex
med langth title corrected
fix in latex in main file
reducing section spacing globally
overview: shortenning
remove repetative coala from section titles
paging: more details and specifics, incl. algo for commit
space enlargements to fill the last page
start updating the coalescing text
put back the old coalecing section
add task splitting, correct the provided example
git push test

\acmConference[Submitted to PLDI'18]{ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 18--22, 2018}{Philadelphia, PA, USA}

@@

%% Some recommended packages.
%\usepackage{booktabs}   %% For formal tables: http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions http://ctan.org/pkg/subcaption
%\usepackage[normalem]{ulem}
%\usepackage{float}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}

@@

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}
\urlstyle{rm}
\linespread{0.98}

@@

% Tighter than defaults:
\setlength{\sectionbelowskip}{1pt}
\setlength{\sectionaboveskip}{5pt plus 1.5pt minus 1.5pt}
\setlength{\subsectionbelowskip}{1pt}
\setlength{\subsectionaboveskip}{3pt plus 1pt minus 1pt}
\setlength{\paragraphaboveskip}{1pt plus 1pt minus 1pt}

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Intermittent Computing $\ldots$}
\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

\section{\sys: Task Coalescing}
\label{sec:task_coalescing}

\input{coalescing}

\section{\sys: Memory Virtualization}
\label{sec:memory_virtulaization}

@@

\section{\sys: Automatic Task Generation}
\label{sec:compiler}

>>>>

\acmConference[Submitted to OOPSLA'18]{ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 18--22, 2018}{Philadelphia, PA, USA}

@@

%% Some recommended packages.
%\usepackage{booktabs}   %% For formal tables: http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions http://ctan.org/pkg/subcaption
%\usepackage[normalem]{ulem}
%\usepackage{float}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{hyphenat}

\usepackage{titlesec}

%\titlespacing{\section}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsection}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsubsection}{0pt}{0.5\baselineskip}{\parskip}
\titlespacing{\section}{2pt}{0.8\baselineskip}{\parskip}
\titlespacing{\subsection}{2pt}{0.6\baselineskip}{\parskip}
\titlespacing{\subsubsection}{2pt}{0.6\baselineskip}{\parskip}

\setlength{\textfloatsep}{5pt}% Remove \textfloatsep

@@

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}

@@

\algnewcommand{\LeftComment}[2][.5\linewidth]{%
  \leavevmode\makebox[#1][l]{$\triangleright$~#2}\hfill}

% Tighter than defaults:
%\setlength{\sectionbelowskip}{1pt}
\setlength{\sectionbelowskip}{4pt}
\setlength{\sectionaboveskip}{5pt plus 1.5pt minus 1.5pt}
\setlength{\subsectionbelowskip}{1pt}
\setlength{\subsectionaboveskip}{3pt plus 1pt minus 1pt}
\setlength{\paragraphaboveskip}{1pt plus 1pt minus 1pt}

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Adaptive Task Coalescing $\ldots$}
\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

\section{Task Coalescing}
\label{sec:task_coalescing}

\input{coalescing}
% \input{newCoalescing}

\section{Memory Virtualization}
\label{sec:memory_virtulaization}

@@

\section{Automatic Task Generation}
\label{sec:compiler}
